---
title: "Lab 1, Team 5"
output:
  html_document: default
  pdf_document: default
---

Find our Lab 1 repository [here](https://github.com/MirandaTilton/Stat585_Lab1)

# Building a Book


1. "pseudo-class"

2. 
* The biggest problem we had when building the book was that there were many required packages that we did not have installed on our machines. To resolve this problem, we downloaded the packages manually. I (Weiquan) wrote a script for scraping the strings that are possible library names and then downloaded them, as well as the dependend libraries. The functionality of the code shows that it efficiently and effectively verifies whether all required libraries have been installed. For those have not been downloaded, the script also attempts to install them.

```{R Libraryscrapping, eval = FALSE}
# Libraryscrapping.r
# scrpping required libraries in the wd and install

setwd(dirname(rstudioapi::getSourceEditorContext()$path))
rm(list=ls())
dev.off()
library(stringr)

# multiple input
temp.Rmd = list.files(pattern="*.Rmd$")
temp.name <-list()
for (i in 1:length(temp.Rmd)){
  temp.name <- append(temp.name, readLines(temp.Rmd[i]))
}

# extract library name
stock1 <- grep("^library\\(.*\\)$", temp.name, value = T)
stock1 <- gsub("library\\(","", stock1)

stock2 <- str_extract_all(temp.name,"[^[:alpha:]]*[[:alpha:]]+[::]{2}[[:alpha:]]+[[:punct:]]?", simplify =T)
stock2 <- as.character(as.vector(stock2))
stock1 <- sapply(strsplit(stock1, split='[^[:alpha:]]', perl=TRUE), function(x) (tail(x, n=1))) # last one
stock2 <- sapply(strsplit(stock2, split='::', fixed=TRUE), function(x) (x[1]))
stock2 <- sapply(strsplit(stock2, split='[^[:alpha:]]', perl=TRUE), function(x) (tail(x, n=1))) # last one

# construct charator vector
package.required <- append(stock1,stock2)
package.required <-unique(package.required)

# Extend to dependent library
package.required <- as.vector(unlist(package_dependencies(package.required)))
package.required <- unique(package.required)

package.required <- package.required[package.required!=("")]
package.required <- package.required[!is.na(package.required)]

# install package
print(package.required)

for (name.packages in package.required) {
  if(!is.element(name.packages, installed.packages()[,1])){
    install.packages(name.packages)
  print(paste("library installed",name.packages))}
  else {print(paste("library installed",name.packages))}
}
```
* while running the condition.rmd file, we have a problem with running the `expect_s3_class(err, "error_bad_argument")`. recommend by the instructor, we use `#` to mask line 786-788. 
* using non-standerize package, $emo$, solution: run `devtools::install_github("hadley/emo")`
* The Rcpp.Rmd require installation of a external tool for C++. Solution for right now is to not evaluate the r chunk in Rcpp.Rmd


# Weather Stations

1. Plot

We begin by loading the appropriate packages and reading in the data. 

```{r, warning = F, message = F}
library(tidyverse)
library(ggplot2)
library(readr)
library(ggmap)
library(maps)
library(mapdata)
weather <- read_fwf("ushcn-v2.5-stations.txt", 
                    fwf_positions(c(1,3,4,6,13,22,33,39,42,94),
                                  c(2,3,5,11,20,30,37,40,71,95), 
                    col_names = c("COUNTRY", "NETWORK", "ID_PLACEHOLDERS",
                                "COOP_ID", "LATITUDE", "LONGITUDE",
                                "ELEVATION", "STATE", "NAME", "TimeZone")),
                    col_types = cols("c","c","c","c","d",
                                     "d","d","c","c","i"))
head(weather)
```

For convenience, we turn the timezone variable into a factor with meaningful labels.

```{r}
weather$TimeZone <- as.factor(weather$TimeZone)
levels(weather$TimeZone) = c("ETS", "CTS","MTS","PTS")
```


We now plot the data on a map with color to indicate elevation and shape to indicate timezone.
```{r}
states <- map_data("state")
ggplot(data = states) + 
  geom_polygon(aes(x = long, y = lat, group = group),
               color = "grey", alpha = 0.6) + 
  geom_point(data = weather,aes(x = LONGITUDE, y = LATITUDE,
                              color = (ELEVATION), shape = TimeZone)) +
  theme_bw() +
  coord_fixed(1.3) +
  guides(fill = FALSE)

```

#More Weather Data
1.Unzip the file
```{r}
#gunzip("ushcn.tavg.latest.raw.tar.gz")
#untar("ushcn.tavg.latest.raw.tar")
```

2. Count the number of files
```{r}
length(list.files("ushcn.v2.5.5.20190130"))
```

3. The coordinates of Fort Dodge, IA are (42.506803,94.180271). We search the weather data for this cordinate.
```{r}
select<- weather %>% 
  filter(LATITUDE>42 & LATITUDE<43 & LONGITUDE< -94 & LONGITUDE> -95)
select
paste(select$COUNTRY[1],select$NETWORK[1],select$ID_PLACEHOLDERS[1],select$COOP_ID[1],".raw.tavg",sep="")
```

